Revisiting the von Bertalanffy Seasonal Cessational Growth Function of Pauly

### 2016-05-22 zzzOld/doc/manuscript_v0_3.Rmd
Moved to Word, Reorganized file strux, added mosquitofish example

# Fitting the Function
## Real Data

@@

>>>>

# Fitting the Function
## Bonito Data

@@

## Mosquitoefish Data

```{r echo=FALSE, results='hide', message=FALSE}
## Bonito data
mqf <- read.csv("Mosquitoefish.csv")
mqf2 <- filterD(mqf,Sitenum==2)
mqf4 <- filterD(mqf,Sitenum==4)
mqf9 <- filterD(mqf,Sitenum==9)
```

```{r echo=FALSE, results='hide', message=FALSE}
## Mosquitofish Site 2

################################################################################
## See if results match that from Emili (Camona-Catot et al. (2014))
lwrbnd <- c(Linf=0,K=0,t0=-Inf,C=0,ts=0)
uprbnd <- c(Linf=Inf,K=Inf,t0=Inf,C=Inf,ts=1)
svmqf2 <- list(Linf=36,K=2,t0=0,C=1.6,ts=0.9)
fitmqf2 <- nls(SL~vbSO(Age2,Linf,K,t0,C,ts),data=mqf2,
               start=svmqf2,lower=lwrbnd,upper=uprbnd,
               algorithm="port",control=list(maxiter=100))
## Linf=35.85, K=2.012, t0=-0.02, C=1.95, and ts=-0.118 ...
## they all match (within rounding) except ts but it is off by +1
cfmqf2 <- cbind(Est=coef(fitmqf2),confint(fitmqf2))
################################################################################

## Fit new model
lwrbnd <- c(Linf=0,Kpr=0,t0=-Inf,ts=0,NGT=0)
uprbnd <- c(Linf=Inf,Kpr=Inf,t0=Inf,ts=1,NGT=1)
svmqf2p <- list(Linf=36,Kpr=2,t0=0,ts=0.9,NGT=0.5)
fitmqf2p <- nls(SL~VBSCGF(Age2,Linf,Kpr,t0,ts,NGT),data=mqf2,
             start=svmqf2p,lower=lwrbnd,upper=uprbnd,
             algorithm="port",control=list(maxiter=100))
cfmqf2p <- cbind(Est=coef(fitmqf2p),confint(fitmqf2p))
```

```{r echo=FALSE, results='hide', message=FALSE}
## Mosquitofish Site 4

################################################################################
## See if results match that from Emili (Camona-Catot et al. (2014))
lwrbnd <- c(Linf=0,K=0,t0=-Inf,C=0,ts=0)
uprbnd <- c(Linf=Inf,K=Inf,t0=Inf,C=Inf,ts=1)
svmqf4 <- list(Linf=36,K=2,t0=0,C=1.6,ts=0.9)
fitmqf4 <- nls(SL~vbSO(Age2,Linf,K,t0,C,ts),data=mqf4,
               start=svmqf4,lower=lwrbnd,upper=uprbnd,
               algorithm="port",control=list(maxiter=100))
## Linf=45.97, K=1.046, t0=-0.197, C=1.28, and ts=0.751 ... They do
cfmqf4 <- cbind(Est=coef(fitmqf4),confint(fitmqf4))
################################################################################

## Fit new model to Mosquitofish Site 5 data
lwrbnd <- c(Linf=0,Kpr=0,t0=-Inf,ts=0,NGT=0)
uprbnd <- c(Linf=Inf,Kpr=Inf,t0=Inf,ts=1,NGT=1)
svmqf4p <- list(Linf=36,Kpr=2,t0=0,ts=0.9,NGT=0.5)
fitmqf4p <- nls(SL~VBSCGF(Age2,Linf,Kpr,t0,ts,NGT),data=mqf4,
             start=svmqf4p,lower=lwrbnd,upper=uprbnd,
             algorithm="port",control=list(maxiter=100))
cfmqf4p <- cbind(Est=coef(fitmqf4p),confint(fitmqf4p))
```

```{r echo=FALSE, results='hide', message=FALSE}
################################################################################
## Purely Demonstration -- Mosquitofish Site 9
## See if results match that from Emili (Camona-Catot et al. (2014))
lwrbnd <- c(Linf=0,K=0,t0=-Inf,C=0,ts=0)
uprbnd <- c(Linf=Inf,K=Inf,t0=Inf,C=Inf,ts=1)
svmqf9 <- list(Linf=36,K=2,t0=0,C=1.6,ts=0.9)
fitmqf9 <- nls(SL~vbSO(Age2,Linf,K,t0,C,ts),data=mqf9,
               start=svmqf9,lower=lwrbnd,upper=uprbnd,
               algorithm="port",control=list(maxiter=100))
## Linf=41.54, K=1.314, t0=-0.214, C=0.621, and ts=-0.717 ... They do
cfmqf9 <- cbind(Est=coef(fitmqf9),confint(fitmqf9))
################################################################################

## Fit new model to Mosquitofish Site 9 data
lwrbnd <- c(Linf=0,Kpr=0,t0=-Inf,ts=0,NGT=0)
uprbnd <- c(Linf=Inf,Kpr=Inf,t0=Inf,ts=1,NGT=1)
svmqf9p <- list(Linf=42,Kpr=1.6,t0=0,ts=0.7,NGT=0.05)
fitmqf9p <- nls(SL~VBSCGF(Age2,Linf,Kpr,t0,ts,NGT),data=mqf9,
             start=svmqf9p,lower=lwrbnd,upper=uprbnd,
             algorithm="port",control=list(maxiter=100))
cfmqf9p <- cbind(Est=coef(fitmqf9p),confint(fitmqf9p))
```
